Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-13 paper/paper.tex
Added preamble file, fixed naming.

\documentclass[letterpaper]{article}
\usepackage[pass]{geometry}

\usepackage{ijcai16}
\usepackage{times}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{mathtools}

\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds}

\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}

\newcommand{\citet}[1]{\citeauthor{#1} \shortcite{#1}}
\newcommand{\citep}[1]{\cite{#1}}

\theoremstyle{definition}
\newtheorem{proposition}{Proposition}

% cref style
\crefname{figure}{Figure}{Figures}
\Crefname{figure}{Figure}{Figures}

% http://tex.stackexchange.com/questions/22100/the-bar-and-overline-commands
\newcommand{\shortoverline}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}

%to do comments
\usepackage{color}
\newcommand{\todo}[1]{{\color{red} {[}{#1}{]}}}

@@

We define a subgraph-except-$k$ isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written
$P \prescript{}{k}{\rightarrowtail} T$ and $P \prescript{}{k}{\hookrightarrow} T$ respectively.

A non-induced subgraph-except-$k$ isomorphism from $P$ to $T$ is equivalent to a subgraph
isomorphism between $P$ and $T$ with $k$ extra universally-adjacent vertices. (However, we can do a
bit better algorithmically.) For induced subgraph-except-$k$ isomorphisms, such an approach cannot
work.

@@

\begin{proposition}
    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
    subgraph-except-$k$ isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
    $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
\end{proposition}
\begin{proof}
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\operatorname{deg}(p) \le \operatorname{deg}(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\operatorname{deg}_{P}(p)-k \le \operatorname{deg}_{P'}(p) \le \operatorname{deg}_{P}(p) \le \operatorname{deg}(t).
\]
\end{proof}

\begin{proposition}
    More powerfully, if $p \prescript{}{k}{\mapsto} t$ then
    $\operatorname{nds}(p)[k+1, k+2, \ldots] \preceq \operatorname{nds}(t)$.
\end{proposition}

@@

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$. The
    vertices $p$ and $q$ in $G^{n, \ell}$ are adjacent, if there are at least $n$ simple paths of
    length exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism
    $P \prescript{}{k}{\rightarrowtail} T$ induces a new subgraph-except-$k$ isomorphism
    $P^{n, 2}\prescript{}{k}{\rightarrowtail} T^{n - k, 2}$.
\end{proposition}

>>>>

\documentclass[letterpaper]{article}

\include{preamble}

@@

We define a $k$-less-subgraph isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written
$P \lessnonind{k} T$ and $P \lessind{k} T$ respectively.

A non-induced $k$-less-subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph
isomorphism between $P$ and $T$ with $k$ extra universally-adjacent vertices. (However, we can do a
bit better algorithmically.) For induced $k$-less-subgraph isomorphisms, such an approach cannot
work.

Let $S$ and $T$ be two sequences. We define $S \preceq T$

@@

\begin{proposition}
    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
    $k$-less-subgraph isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
    $\deg(p) \le \deg(t) + k$.
\end{proposition}
\begin{proof}
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t).
\]
\end{proof}

\begin{proposition}
    More powerfully, if $p \prescript{}{k}{\mapsto} t$ then
    $\nds(p)[k+1, k+2, \ldots] \preceq \nds(t)$.
\end{proposition}

\begin{proof}
Let

\end{proof}

@@

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$. The
    vertices $p$ and $q$ in $G^{n, \ell}$ are adjacent, if there are at least $n$ simple paths of
    length exactly $\ell$ between $p$ and $q$ in $G$. Then any $k$-less-subgraph isomorphism
    $P \lessnonind{k} T$ induces a new $k$-less-subgraph isomorphism
    $P^{n, 2}\lessnonind{k} T^{n - k, 2}$.
\end{proposition}
